### 2020-04-05 scache/jpdc/tex/evaluation.tex
jpdc
some minor fixes
update

@@

% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big data analysis. 
{\color{black}
This section reveals a representative evaluation of SCache performance on both Spark and Hadoop MapReduce.
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big data analysis.
In industrial big data, SQL-based big data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
% SQL-Based Big Data Systems are widely used on industrial application.
% Because of the limited time and resource, 
To prove the performance gain of SCache in industry, 
we evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/}.
TPC-DS is a standard benchmark which focuses on modeling industrial workload.
% TPC-DS, TPCx-BB, HiBench, BigDataBenchmark, and so on are popular standard big data benchmarks which evaluate big data systems.
% TPC-DS models queries and data maintenance of a retail product supplier and provides a representative evaluation of performance.
% We believe using TPC-DS is able to evaluate the performance of SCache in industry. 
% First, we evaluate the Spark with SCache in two different benchmarks.
% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Finally, we measure the overhead of weighted reservoir sampling. 
% In summary, SCache decreases ~$89\%$ time of Spark shuffle without introducing extra network transfer.
% More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by SCache.
%  applying the optimization from SCache.
In summary, SCache decreases ~$89\%$ time of Spark shuffle and improves ~$40\%$ of the overall completion time of TPC-DS on average.
Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
}

@@

% The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% % As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
% In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
% So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
% In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
% By doing this, Spark minimizes the shuffle data through network. 
% At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
% It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\includegraphics[width=.8\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

\subsubsection{Industrial Production Workload}
% We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
% TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
% TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
TPC-DS\footnote{http://www.tpc.org/tpcds/} contains 99 queries and is considered as a standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in some shuffle-heavy queries, Spark with SCache outperforms original Spark by an order of magnitude. 
% It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

@@

{\color{black}
\subsection{Hadoop MapReduce with SCache}

{\color{black}
% To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
% Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
Unlike Spark, Hadoop MapReduce has only one Map and one Reduce phase.
Such a simple workflow alleviates the defect of the naive scheduling schemes and reduces the benefits of \textit{pre-scheduling}.
However, SCache can still provide considerable optimization on shuffle-heavy workloads.
We use Terasort benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
% Although the simple workflow alleviates the benefits of \textit{pre-scheduling}, SCache can still .
% Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
}

As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache starts shuffle and reduce simultaneously.
% writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck.
This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache decouples shuffle from reduce and starts pre-fetching in the map phase.
% This avoids the reduce phase waiting for the shuffle data.
SCache utilizes the idle I/O throughput in the map phase.
As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

% \subsection{Performance Analysis}\label{model_performance_analysis}

% \begin{table*}[!t]

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=.8\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

@@

% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big data analysis. 
{\color{black}
This section reveals a representative evaluation of SCache performance on both Spark and Hadoop MapReduce.
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big data analysis.
In industrial big data, SQL-based big data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
% SQL-Based Big Data Systems are widely used on industrial application.
% Because of the limited time and resource,

% To prove the performance gain of SCache in industry, 
We \edited{first} evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/} \edited{to prove the performance gain of SCache in industry}.
TPC-DS is a standard benchmark which focuses on modeling industrial workload.
% TPC-DS, TPCx-BB, HiBench, BigDataBenchmark, and so on are popular standard big data benchmarks which evaluate big data systems.
% TPC-DS models queries and data maintenance of a retail product supplier and provides a representative evaluation of performance.
% We believe using TPC-DS is able to evaluate the performance of SCache in industry. 
% First, we evaluate the Spark with SCache in two different benchmarks.
% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
\edited{Then we use a recognized shuffle intensive benchmark Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.}
% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Finally, we measure the overhead of weighted reservoir sampling. 
% In summary, SCache decreases ~$89\%$ time of Spark shuffle without introducing extra network transfer.
% More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by SCache.
%  applying the optimization from SCache.
In summary, SCache decreases ~$89\%$ time of Spark shuffle and improves ~$40\%$ of the overall completion time of TPC-DS on average.
Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
}

@@

% The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% % As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
% In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
% So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
% In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
% By doing this, Spark minimizes the shuffle data through network. 
% At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
% It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load.

\subsubsection{Industrial Production Workload}
\edited{
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.).}
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to \edited{compatible issues}. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in some shuffle-heavy queries, Spark with SCache outperforms original Spark by an order of magnitude. 
% It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

@@

\subsection{Hadoop MapReduce with SCache}

% To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
% Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
Unlike Spark, Hadoop MapReduce has only one Map and one Reduce phase.
Such a simple workflow alleviates the defect of the naive scheduling schemes and reduces the benefits of \textit{pre-scheduling}.
However, SCache can still provide considerable optimization on shuffle-heavy workloads.

We use Terasort \edited{\cite{spark-tera}} benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
\edited{Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
The second shuffle partitions the data through a Spark \texttt{RangePartitioner}. 
}
% Although the simple workflow alleviates the benefits of \textit{pre-scheduling}, SCache can still .
% Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size.

As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache starts shuffle and reduce simultaneously.
% writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck.
This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache decouples shuffle from reduce and starts pre-fetching in the map phase.
% This avoids the reduce phase waiting for the shuffle data.
SCache utilizes the idle I/O throughput in the map phase.
As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.

@@

### 2020-04-05 scache/jpdc/tex/impl.tex
update

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCache records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{black}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

@@

{\color{black}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
For now, SCache only restarts failed workers without recovering their data.
SCache leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

>>>>

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCache records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, \edited{which is defined by the memory usage,} the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

@@

{\color{black}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
\edited{Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once),}
% For now, 
SCache only restarts failed workers without recovering their data \edited{and} leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the \edited{\texttt{getBlock}} API will return a \edited{data-not-found} error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.

\edited{We believe that }

A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

### 2020-04-05 scache/jpdc/tex/optimization.tex
update

{\color{black}
\subsection{Observations}\label{observation}
% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, shuffle introduces an explicit overhead during shuffle read.
% Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
% because all reduce tasks start shuffle read simultaneously, 
Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.

% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\). \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase. 
% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
\begin{itemize}
	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
\end{itemize}
% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
}

@@

\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor\newline
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.\newline
		% \State Return if it is impossible.
		\Return
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

>>>>

% {\color{black}
% \subsection{Observations}\label{observation}
% % DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory

% In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
% For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
% In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
% On the reduce side, shuffle introduces an explicit overhead during shuffle read.
% % Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
% % because all reduce tasks start shuffle read simultaneously, 
% Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.

% % To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\). \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase. 
% % We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
% % In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
% To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
% \begin{itemize}
% 	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
% 	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
% \end{itemize}
% % In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
% }

@@

\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor\newline
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.\newline
		% \State Return if it is impossible.
		\Return
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
